Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-07 paper.qmd
Updated the Five Gaussian cluster example

## Compute hexbin parameters
num_bins_x_gau1 <- 17
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

distance_df_small_edges_gau1 <- distance_gau1 |>
  filter(distance < benchmark_gau1)

@@

## Set the maximum difference as the criteria
distance_df_small_edges <- distance_gau1 |>
  dplyr::filter(distance < benchmark_gau1)
```

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 52
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

distance_df_small_edges_gau1 <- distance_gau1 |>
  filter(distance < benchmark_gau1) |>
  mutate(ID = row_number()) #|>
  #filter(!(ID %in% c(112)))

@@

## Set the maximum difference as the criteria
distance_df_small_edges <- distance_gau1 |>
  dplyr::filter(distance < benchmark_gau1)

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 20
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

distance_df_small_edges_gau1 <- distance_gau1 |>
  filter(distance < benchmark_gau1) #|>
  #mutate(ID = row_number()) #|>
  #filter(!(ID %in% c(97)))

@@

## Set the maximum difference as the criteria
distance_df_small_edges <- distance_gau1 |>
  dplyr::filter(distance < benchmark_gau1)
```

>>>>

## Compute hexbin parameters
num_bins_x_gau1 <- 14
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

distance_df_small_edges_gau1 <- distance_gau1 |>
  filter(distance < 0.1) #benchmark_gau1

distance_df_small_edges_gau1 <- distance_df_small_edges_gau1 |>
  mutate(ID = row_number()) |>
  dplyr::filter(!(ID %in% c(150, 110))) |>
  dplyr::select(-ID)

tr_from_to_df_gau1 <- right_join(
  tr_from_to_df_gau1, distance_df_small_edges_gau1, 
  by = c("from", "to"))

@@

## Set the maximum difference as the criteria
distance_df_small_edges <- distance_gau1 |>
  dplyr::filter(distance < 0.1) |>
  mutate(ID = row_number()) |>
  filter(!(ID %in% c(150, 110))) |>
  dplyr::select(-ID) #benchmark_gau1
```

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 50
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

distance_df_small_edges_gau1 <- distance_gau1 |>
  filter(distance < 0.05) #|> benchmark_gau1
  #mutate(ID = row_number()) #|>
  #filter(!(ID %in% c(112)))

@@

## Set the maximum difference as the criteria
distance_df_small_edges <- distance_gau1 |>
  dplyr::filter(distance < 0.05) #benchmark_gau1

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 22
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

distance_df_small_edges_gau1 <- distance_gau1 |>
  filter(distance < 0.06) #|> #benchmark_gau1
  #mutate(ID = row_number()) #|>
  #filter(!(ID %in% c(97)))

tr_from_to_df_gau1 <- right_join(
  tr_from_to_df_gau1, distance_df_small_edges_gau1, 
  by = c("from", "to"))

@@

## Set the maximum difference as the criteria
distance_df_small_edges <- distance_gau1 |>
  dplyr::filter(distance < 0.06) #benchmark_gau1 #benchmark_gau1
```
